What's in a name? On the automated topic naming of software maintenance activities

### 2010-03-06 icpc/icpc2010.tex
unsupervised

In general, this approach did not work out well as common labels dominated the less common labels. The related words for \emph{correctness}, for example, tended to be too lengthy and non-specific. Table \ref{tbl:wordlist} lists results. A \emph{named   topic} is a topic with a matching label. There are \{periods X 20\} topics per project. All experiments were run on MaxDB and MySQL data.

@@

For \textsf{exp2}, there are many more unnamed topics. Only reliability produces a lot of matches, mostly with the `error' word. Co-occurrence results were poor.

@@

\subsection{Analysis the unsupervised labelling}

@@

Based on the labels, and our manual topic labelling, we compared the results of the unsupervised word matching approach. For each quality we tried to assess whether the manual tag matched the unsupervised label assigned. Table \ref{tbl:maxdb-unsup-results} shows our results for MaxDB and MySQL. In general results are poor. Using the F-Measure, the weighted average of precision and recall, where 1 is perfect, our best results are 0.6, a few at 0.4, and most around 0.2. Similar results using the Matthew's correlation coefficient (used to measure efficacy where classes are of different sizes), and the receiver operating characteristic area under curve.

@@

We took our annotated dataset and applied supervised learner to it. Because our dataset was of word counts we expected Bayesian techniques, often used in spam filtering, to perform well. We also tried other learners that WEKA~\cite{weka09} provides: rule learners, tree learners, vector space learners, and support vector machines.  Table \ref{tab:best-learn-per-tag} shows the performance of the best performing learner per label.  We considered the best learner for a label to be the one which had the highest ROC value for that label. Table \ref{tab:best-learn-per-tag} shows the ROC value, the accuracy of a ZeroR learner ( a learner which just chooses the largest category all of the time), the difference in accuracy between the best learner and ZeroR, and the F-measure for that particular learner. The ZeroR difference is often negative, but in particular for labels which are not as common this can be expected because any miscategorization will hurt accuracy, this is why the F1 (F-measure) and the ROC values are useful as they can better present performance on labels which are not applicable to the majority of samples.

>>>>

In general, this approach did not work out well as common labels dominated the less common labels. The related words for \emph{correctness}, for example, tended to be too lengthy and non-specific. Table \ref{tbl:wordlist} lists results. A \emph{named   topic} is a topic with a matching label. There are \{periods X 20\} topics per project as we told LDA to extract 20 topics per period. All experiments were run on MaxDB 7.500 and MySQL 3.23 data.

@@

For \textsf{exp2}, there are many more unnamed topics. Only reliability produces a lot of matches, mostly with the word `error'. Co-occurrence results were poor.

@@

\subsection{Analysis of the unsupervised labelling}

@@

Based on the labels, and our manual topic labelling, we compared the results of the unsupervised word matching approach. For each quality we tried to assess whether the manual tag matched the unsupervised label assigned. Table \ref{tbl:maxdb-unsup-results} shows our results for MaxDB and MySQL. In general results are poor. Using the F-Measure, the weighted average of precision and recall, where 1 is perfect, our best results are 0.6, a few at 0.4, and most around 0.2. We achieved similar results using the Matthew's correlation coefficient (used to measure efficacy where classes are of different sizes) and ROC.

Based on these results we find that reliability and usability worked well for MaxDB in \textsf{exp2} and better in \textsf{exp3}. MySQL reasonable results within \textsf{exp2} were for reliability and efficiency. MySQL's results for efficiency did not improve in \textsf{exp3} but other qualities such as functionality did improve. If a \emph{C} grade performance has a ROC value of $0.6$ then most of these tests scored \emph{C} or less, but our results were still better than random chance.

@@

We took our annotated dataset and applied supervised learners to it. Because our dataset was of word counts we expected Bayesian techniques, often used in spam filtering, to perform well. We also tried other learners that WEKA~\cite{weka09} provides: rule learners, tree learners, vector space learners, and support vector machines.  Table \ref{tab:best-learn-per-tag} shows the performance of the best performing learner per label.  We considered the best learner for a label to be the one which had the highest ROC value for that label. Table \ref{tab:best-learn-per-tag} shows the ROC value, the accuracy of a ZeroR learner ( a learner which just chooses the largest category all of the time), the difference in accuracy between the best learner and ZeroR, and the F-measure for that particular learner. The ZeroR difference is often negative, but in particular for labels which are not as common this can be expected because any miscategorization will hurt accuracy, this is why the F1 (F-measure) and the ROC values are useful as they can better present performance on labels which are not applicable to the majority of samples.
